Rmarkdown Features

### 2018-05-19 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

```{yaml}
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    code_folding: hide
    fig_width: 7
    fig_height: 6
    toc: true
    toc_depth: 4
    toc_float: true
```

@@

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```yaml
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt
---
```

@@

```tex
%加這個就可以設定字體
\usepackage{fontspec}
%使用xeCJK，其他的還有CJK或是xCJK
\usepackage{xeCJK}

@@

@@

Add `results='asis'` to r code chunk option.
```{r results='asis'}
library(mat2tex)
mt <- c(1,2)
"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
```

@@

![](mat2tex.png){width=100% height=auto}

@@

Bibliographies & Citations{#cite} 
-----------------------------

>>>>

```{yaml}
output:
  html_document:
    includes:
        before_body: mathjax_bm.tex
    css: ../style_sheets/style.css
    df_print: kable
    code_folding: hide
    fig_width: 7
    fig_height: 6
    toc: true
    toc_depth: 4
    toc_float: true
```

@@

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```{yaml}
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt
geometry: a5paper, headheight=0pt, margin=0.4in
---
```

@@

```{tex}
%加這個就可以設定字體
\usepackage{fontspec}
%使用xeCJK，其他的還有CJK或是xCJK
\usepackage{xeCJK}

\usepackage{multicol}
\usepackage{bm}

@@

knitr Parameters
--------------------------------

### Root
```r
knitr::opts_knit$set(root.dir='..')
```
The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default. In the case above, I changed it to  the **directory that is parent to the default directory**.

### Code Chunk & Figure Options
```r
library(svglite) 
knitr::opts_chunk$set(
	echo = FALSE, # No display code chunks
	message = FALSE,
	warning = FALSE,
	dev='svg', # or 'svglite' for multibite characters
	comment="",
	fig.dim = c(3.5, 3.5)  # (width, height)
)
options(digits = 2) # auto round to 2 decimals when printed
```

@@

Add `results='asis'` to r code chunk option.

````r
`r ''````{r results='asis', echo=FALSE}
library(mat2tex)
mt <- c(1,2)
"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
```
````

```{r echo=FALSE, results='asis'}
library(mat2tex)
mt <- c(1,2)
"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
```

@@

````r
This is the variable `mt`,
`r ''````{r results='asis', echo=FALSE}
library(mat2tex)
mt <- matrix(1:4, 2,2)
"$A =" %_% xm(mt,0) %_%"^{-1}$"
```
, which is a matrix.
````

@@

Display Code Chunk with Code Chunk
--------------------------------------------

```{r include=F}
code <- htmltools::HTML("<code>`r ''`</code>")
```

Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:

`````rmd
````Rmd
`r code````{r}
Some R Code
```
````
`````

The code `r code` is for suppressing the execution of the r code chunk after it.

Bibliographies & Citations{#cite} 
-----------------------------------------
